Turbulence in compact to giant HII regions

### 2022-02-03 strucfunc_paper.tex
Begin rewrite of model strucfunc section

We will also employ the related quantity of the
normalized spatial autocovariance or autocorrelation function:
\begin{equation}
  \label{eq:autocovar}
  C(r) = \frac{1}{\sigma^2\pos}\left\langle 
  \bigl[
  V_{c}(\xx_j) \  V_{c}(\xx_i)
  \bigr]^{2} \right \rangle_{\Abs{\xx_j - \xx_i\!} \ \approx \ r} \ .
\end{equation}
If the fluctuations are perfectly spatially homogeneous, then the
two quantities are related \citep{1984ApJ...277..556S} as
\begin{equation}\label{eq:functional}
  B(r) = 2\sigma^2\pos \bigl[   1 - C(r)\bigr] .
\end{equation}
In less ideal situations, then \(B(r)\) is to be preferred since it is
relatively unaffected by non-stationary effects \citep{1984ApJ...277..556S}.
Nonetheless, \(C(r)\) is more amenable to heuristic reasoning in some cases,
which we will take advantage of below.

\subsection{Application to our HII regions sample}\label{sec:methods-apply}

The autocovariance function:

\begin{equation}\label{eq:Cr}
C(\boldsymbol{r}) = \dfrac{\sum_{\text{pairs}}[V_{c}(\xx + \boldsymbol{r}) \times V_{c}(\xx) ]} {N(\boldsymbol{r})}
\end{equation}
%
is another statistical tool used in studying the turbulent flows.
The interpretation of the Equation \ref{eq:Cr} depends on the assumption of homogeneity, which may be violated for astrophysical processes.
Because of this, Equation \ref{eq:Br} is a better approach to characterize the velocity fluctuations even in the presence of large scale linear gradients and may be sensitive to a wider range of scales \citep{1984ApJ...277..556S}.

For an homogeneous random field equations \ref{eq:Br} and \ref{eq:Cr} are related by:

\begin{equation}\label{eq:functional}
B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

We use a new functional for the structure function based on equation \ref{eq:functional}. 
First we propose a new \(C(r)\) in the form:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r; r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
\end{equation}
%
The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
\citet{1984ApJ...277..556S}.

>>>>

We will also employ the related quantity of the
normalized spatial autocovariance or autocorrelation function:
\begin{equation}
  \label{eq:autocovar}
  C(r) = \frac{1}{\sigma^2\pos}\left\langle 
  \bigl[
  V_{c}(\xx_j) \  V_{c}(\xx_i)
  \bigr]^{2} \right \rangle_{\Abs{\xx_j - \xx_i\!} \ \approx \ r} \ .
\end{equation}
If the fluctuations are perfectly spatially homogeneous, then the
two quantities are related \citep{1984ApJ...277..556S} as
\begin{equation}\label{eq:functional}
  B(r) = 2\sigma^2\pos \bigl[   1 - C(r)\bigr] .
\end{equation}
In less ideal situations, then \(B(r)\) is to be preferred since it is
relatively unaffected by non-stationary effects
such as large-scale linear gradients 
\citep{1984ApJ...277..556S}.
Nonetheless, \(C(r)\) is more amenable to heuristic reasoning in some cases,
which we will take advantage of below.

\subsection{A heuristic model for the structure function}\label{sec:methods-apply}

A common property of homogeneous fluctuating velocity fields is that neighboring points tend to have similar velocities
(\(C(r) \approx 1\) for small \(r\)),
whereas points that are far apart may have very different velocities
(\(C(r) \ll 1\) for large \(r\)).
The value of the separation that corresponds to
the transition between these two regimes
is called the correlation length, \(r_0\).
In the simplest case,
two points separated by \(r \gg r_0\) have totally uncorrelated velocities
in the sense that knowledge of the velocity at the first point is of
no help in predicting the velocity at the second point.
At scales smaller than \(r_0\), the fluctuations often show a power-law behavior.

We therefore propose the following 2-parameter model
for the autocorrelation function:
%
\begin{equation}\label{eq:new-correlation-form}
  C(r;\ r_0, m) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right].
\end{equation}
%
in which \(r_{0}\)\ is the correlation length (see above)
and \(m\) is the power-law slope at small scales.
This is constructed so that \(C(r) = 1/2\) at \(r = r_0\),
while the exponential form ensures that \(C(r)\) rapidly approaches zero
for larger separations.

The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
\citet{1984ApJ...277..556S}.
